---
---
title: "Reporting item bank datapage"
subtitle: "Interactive exploration of reporting items and concepts across evidence synthesis guidelines"
format:
  html:
    theme: cosmo
    toc: true
    toc-location: left
    page-layout: full
    css: styles.css
    output-file: index
execute:
  echo: false
  message: false
  warning: false
---
---

```{r setup}
#| include: false

knitr::opts_chunk$set(message = FALSE, warning = FALSE)

suppressPackageStartupMessages({
  library(here)
  library(readr)
  library(dplyr)
  library(DT)
  library(crosstalk)
  library(htmltools)
})

clean_utf8 <- function(df) {
  df |>
    mutate(across(where(is.character), ~ iconv(.x, from = "", to = "UTF-8", sub = "byte")))
}

stat_card <- function(value, label) {
  div(
    class = "stat-card",
    span(class = "stat-value", format(value, big.mark = ",")),
    span(class = "stat-label", label)
  )
}

dt_buttons <- function(filename_stub) {
  list(
    list(
      extend = "collection",
      text = "⬇ Download filtered",
      buttons = list(
        list(
          extend = "csv",
          text = "CSV",
          filename = filename_stub,
          exportOptions = list(
            columns = ":visible",
            modifier = list(search = "applied")
          )
        ),
        list(
          extend = "excel",
          text = "Excel",
          filename = filename_stub,
          exportOptions = list(
            columns = ":visible",
            modifier = list(search = "applied")
          )
        ),
        list(
          extend = "copy",
          text = "Copy",
          exportOptions = list(
            columns = ":visible",
            modifier = list(search = "applied")
          )
        )
      )
    ),
    list(extend = "colvis", text = "Columns ▾")
  )
}

dt_options <- function(filename_stub) {
  list(
    dom = "Bfrtip",
    buttons = dt_buttons(filename_stub),
    pageLength = 10,
    lengthMenu = list(c(10, 25, 50, 100, -1), c("10", "25", "50", "100", "All")),
    autoWidth = TRUE,
    scrollX = TRUE,
    deferRender = TRUE,
    searchDelay = 350,
    language = list(search = "Search all columns:")
  )
}
```

```{=html}
<style>
body { font-size: 15px; }
h2 { border-bottom: 2px solid #e9ecef; padding-bottom: 0.3rem; margin-top: 2.5rem; }

.stat-card-row {
  display: flex;
  gap: 1rem;
  flex-wrap: wrap;
  margin: 1rem 0 1.25rem;
}
.stat-card {
  flex: 1 1 180px;
  background: #f8f9fa;
  border: 1px solid #e9ecef;
  border-radius: 0.6rem;
  padding: 0.9rem 1.1rem;
}
.stat-value {
  font-size: 1.55rem;
  font-weight: 700;
  color: #2c3e50;
  display: block;
  line-height: 1.1;
}
.stat-label {
  font-size: 0.8rem;
  color: #6c757d;
  text-transform: uppercase;
  letter-spacing: 0.03em;
}

.filter-panel {
  background: #ffffff;
  border: 1px solid #dee2e6;
  border-radius: 0.7rem;
  padding: 1rem 1.15rem 0.85rem;
  margin-bottom: 1.1rem;
  box-shadow: 0 1px 4px rgba(0,0,0,0.05);
}
.filter-panel-title {
  font-weight: 700;
  font-size: 0.95rem;
  color: #495057;
  margin-bottom: 0.8rem;
  display: flex;
  align-items: center;
  justify-content: space-between;
  gap: 1rem;
}
.filter-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(220px, 1fr));
  gap: 1rem 1.25rem;
}
.filter-grid label {
  font-weight: 600;
  font-size: 0.85rem;
  color: #495057;
}

.reset-btn {
  font-size: 0.78rem;
  padding: 0.15rem 0.6rem;
  border-radius: 1rem;
}

.result-count {
  font-size: 0.9rem;
  color: #6c757d;
  margin: 0.25rem 0 1rem;
}
.result-count strong { color: #2c3e50; }

.crosstalk-input.crosstalk-input-select .selectize-control.single .selectize-input {
  position: relative;
  padding-right: 2rem;
}
.crosstalk-input.crosstalk-input-select .selectize-control.single .selectize-input::after {
  content: "▾";
  position: absolute;
  right: 0.75rem;
  top: 50%;
  transform: translateY(-50%);
  pointer-events: none;
  color: #555;
  font-size: 0.85em;
}

.download-buttons {
  margin: 1rem 0 1.75rem;
  display: flex;
  gap: 0.75rem;
  flex-wrap: wrap;
  justify-content: center;
}
.download-buttons .btn {
  border-radius: 0.45rem;
  font-size: 0.86rem;
}

.dataTables_wrapper .dt-buttons { margin-bottom: 0.5rem; }
table.dataTable thead th {
  background-color: #2c3e50;
  color: #fff;
}
.table-note {
  font-size: 0.9rem;
  color: #6c757d;
  margin-top: 0.35rem;
}
</style>
```

## Background

This datapage accompanies a systematic compilation of reporting items from evidence synthesis reporting guidelines. It provides a harmonized **item bank** and **concept-level dataset** that can be filtered by guideline, methodology, and discipline, and exported for reuse.

::: callout-note
## How to use this page

- Use the **Item bank** tab for individual reporting items and the **Concepts** tab for standardized concept mappings.
- Filter with the controls above each table. Filters combine with AND logic.
- Search within specific columns using the table header boxes, or use the global search box.
- Use **⬇ Download filtered** for the current filtered view, or the full-dataset buttons for everything.
:::

## Datasets {.panel-tabset}

### Item bank

```{r load-items}
data <- read_csv(
  here("data", "item_bank_reporting_guideline_compiled.csv"),
  locale = locale(encoding = "UTF-8")
) |>
  clean_utf8()

study <- read_csv(
  here("data", "item_bank_reporting_guideline.csv"),
  locale = locale(encoding = "UTF-8")
) |>
  clean_utf8()

items_joined <- data |>
  left_join(
    study |>
      select(study_id, methodology_category, discipline),
    by = "study_id"
  ) |>
  rename(
    guideline = checklist,
    methodology = methodology_category
  ) |>
  mutate(
    guideline = as.factor(guideline),
    methodology = as.factor(methodology),
    discipline = as.factor(discipline)
  )

items_display <- items_joined |>
  select(
    guideline,
    study_id,
    checklist_item_id,
    methodology,
    discipline,
    section,
    topic,
    reporting_item_number,
    reporting_item,
    standardised_section,
    language
  ) |>
  clean_utf8()

sd_items <- SharedData$new(
  items_display,
  key = ~checklist_item_id,
  group = "items"
)
```

::: {.filter-panel}
::: {.filter-panel-title}
Filter the item bank
<button class="btn btn-outline-secondary reset-btn" onclick="location.reload()">Reset filters ↺</button>
:::
::: {.filter-grid}
```{r items-filters}
filter_select("guideline_items", "Guideline", sd_items, ~guideline, multiple = TRUE)
filter_select("methodology_items", "Methodology", sd_items, ~methodology, multiple = TRUE)
filter_select("discipline_items", "Discipline", sd_items, ~discipline, multiple = TRUE)
```
:::
:::

<div class="result-count">Use the filters and table search to narrow the view. The table below starts with <strong>10 rows</strong> per page.</div>

```{r items-table}
datatable(
  sd_items,
  filter = "top",
  extensions = c("Buttons"),
  rownames = FALSE,
  options = dt_options("item_bank_filtered")
)
```

<div class="table-note">The filtered download exports the currently matched rows, not just the visible page.</div>

**Download full item bank datasets (all rows, unfiltered):**

<div class="download-buttons">
[⬇ Full item bank CSV](../data/item_bank_reporting_guideline_compiled.csv){.btn .btn-primary .btn-sm role="button"}
</div>

### Concepts

```{r load-concepts}
concept <- read_csv(
  here("data", "item_bank_reporting_guideline_concepts.csv"),
  locale = locale(encoding = "UTF-8")
) |>
  clean_utf8()

concept_joined <- concept |>
  left_join(
    study |>
      select(study_id, methodology_category, discipline),
    by = "study_id"
  ) |>
  rename(
    guideline = checklist,
    methodology = methodology_category
  ) |>
  mutate(
    guideline = as.factor(guideline),
    methodology = as.factor(methodology),
    discipline = as.factor(discipline)
  )

concept_display <- concept_joined |>
  select(
    study_id,
    guideline,
    checklist_item_id,
    methodology,
    discipline,
    section,
    topic,
    reporting_item_number,
    standardised_reporting_item_elements,
    standardised_section,
    standardised_subsection
  ) |>
  clean_utf8()

sd_concepts <- SharedData$new(
  concept_display,
  key = ~paste(checklist_item_id, reporting_item_number),
  group = "concepts"
)
```

::: {.filter-panel}
::: {.filter-panel-title}
Filter the concept dataset
<button class="btn btn-outline-secondary reset-btn" onclick="location.reload()">Reset filters ↺</button>
:::
::: {.filter-grid}
```{r concepts-filters}
filter_select("guideline_concepts", "Guideline", sd_concepts, ~guideline, multiple = TRUE)
filter_select("methodology_concepts", "Methodology", sd_concepts, ~methodology, multiple = TRUE)
filter_select("discipline_concepts", "Discipline", sd_concepts, ~discipline, multiple = TRUE)
```
:::
:::

<div class="result-count">Use the filters and table search to narrow the view. The table below starts with <strong>10 rows</strong> per page.</div>

```{r concepts-table}
datatable(
  sd_concepts,
  filter = "top",
  extensions = c("Buttons"),
  rownames = FALSE,
  options = dt_options("concepts_filtered")
)
```

<div class="table-note">The filtered download exports the currently matched rows, not just the visible page.</div>

**Download full concept dataset (all rows, unfiltered):**

<div class="download-buttons">
[⬇ Full concepts CSV](../data/item_bank_reporting_guideline_long_pilot.csv){.btn .btn-primary .btn-sm role="button"}
</div>

## Citation and reuse

If you use these data, please cite:

> [Add full paper citation here.]

You are encouraged to fork or clone the GitHub repository backing this datapage, open issues for suggested improvements or corrections, and contribute extensions.